The Place of the Local Group in the Cosmic Web

### 2014-08-07 paper/main.tex
new version

\begin{abstract}
We explore the characteristics of the Local Group (LG)
location in the cosmic web using a cosmological simulation in the
$\Lambda$CDM cosmology.  We use the Hessian of the gravitational
potential to define the cosmic web, where regions are classified as
either peak, sheet, filament or void.  The LG in the simulations are
split into two samples.  The first is a general sample composed by
halo pairs with similar masses and isolation criteria as observed in
the LG.  The second is a subset with additional kinematic constaints.
We find that the pairs in the LG sample with all constraints are: i)
Preferentially located in filaments and sheets, ii) located in in a
narrow range of local overdensity $0<\delta<4$, web ellipticity
$0.1<e<1.0$ and prolateness $-0.5<p<0.5$.  iii) Clearly aligned with
the cosmic web, in particular for pairs in filaments/sheets the
orbital angular momentum tends to be perpendicular to the filament
direction or the sheet plane. A stronger alignment is present for the
vector linking the two halos, which lies along the filament or the
sheet plane.  We show that the first and second results are expected
trends with the LG total mass.  However, the strong alignment with the
cosmic web cannot be explained in the same way.

@@

\subsection{Alignment along the cosmic web}

We now study the alignment of the LG with respect to the cosmic web.

\subsubsection{Orbital Angular Momentum}

Figure \ref{fig:alignment_n} and \ref{fig:alignment_r} show  the main result of that study.
They present the cumulative distribution of
$\mu\equiv\hat{e}_i\cdot\hat{n}$ and $\mu\equiv\hat{e}_i\cdot\hat{r}$
for the three eigenvectors $i=1,2,3$.   
Lines in each panel correspond to different samples.
The straight line across the diagonal shows the expected
result for vectors with randomly distributed directions.

For the alignment of $\hat{n}$ in Figure \ref{fig:alignment_n} there
are two important features.
First the alignments themselves. 
There is a strong anti-alignment signature between $\hat{n}$ and the
third eigenvector. 
With respect to the second eigenvector the distribution is consistent
with no aligment. 
For the first eigenvector there is a strong alignment, an expected
result after considering the results with the other eigenvectors and
keeping in mind that the eigenvectors are orthonormal.
Second, the alignment strenght changes for the different samples. 
For the anti-alignment with $\hat{e}_3$ the signal strenghtens as we
move from the GS to the 3$\sigma$ into the 2$\sigma$ sample.

Quantitatively, the anti-alignment feature found with the $\hat{e}_3$ 
vector means that for 2$\sigma$ sample, $\sim 50\%$ pairs have
$|\mu|<0.2$ ($78$ degrees angle), and $\sim 75\%$ pairs have $|\mu|<0.4$
($66$ degrees angle). 
These signals do not change significantly on
different environments as has been already show in different alignment
studies that similar \citep{Libeskind2013} or identical
\citep{ForeroRomero2014} web finding techniques as ours.
In particular  these trends hold for pairs in filaments and walls.
If we consider only pairs in filaments, we have that the pair orbital
angular momentum tends to be perpendicular to the filament direction,
in the case of sheets it tends to lie within the sheet plane.

@@

\subsubsection{Radial motion}

For the alignment of $\hat{r}$ in Figure \ref{fig:alignment_r} there
are similar features as in the case of $\hat{n}$. 
In this case we find that the vector $\hat{r}$
is strongly aligned along the direction defined by
$\hat{e}_3$ and anti-aligned along $\hat{e}_1$; correspondingly the
signal along $\hat{e}_2$ is rather weak.

In this case we also find a stronger signal as we move into more restrictive
samples, although the signal from the GS is already very
significant. Quantitatively, the alignment feature with $\hat{e}_3$
means that for the 2$\sigma$ and 3$\sigma$ samples, $\sim 50\%$ pairs
have $|\mu|>0.8$ ($36$ degrees angle) and $\sim 25\%$ pairs have
$|\mu|<0.95$ ($18$ degrees angle).

@@

\subsubsection{Halo Spin}

We also explore the alignment of the  angular momentum (spin) of each pair
member $\hat{j}_A$ and $\hat{j}_B$ with each other, the orbital
angular momentum and with the cosmic web.

Figure \ref{fig:jj_alignment} shows the cumulative distribution of dot
product between angular momentum of the  two halos. We find a a slight alignment
of spin vectors for the $2\sigma$ sample with a median aroung
$|\mu|\sim 0.7$ ($45$ degrees) However, we found no significant
alignment with the orbital angular momentum or the cosmic web.

@@

We explored the characteristics of the LG location in the cosmic web.

LG pairs are preferentially located in filaments and sheets. The mass range
of the pairs sample plays an important role in the fractions for each environment
type as shown in table $1$ and figure $1$.

There is a clear anti-alignment between the third eigenvector and the vector normal 
to the pair orbital plane. This feature is not mass dependant as can be shown in
figure $3$.
For pairs in filaments this means the pair orbit tends to be perpendicular to the 
filament direction, and both pair members lie along the filament, and in the case 
of pairs in sheets, we have the pair orbital plane lie in the sheet plane.
We also found this anti-alignment becomes stronger for the samples being more 
closely related to the LG, it means it is stronger for $2\sigma$ sample.
All these alignment features are consistent with pair orbits relaxing their 
movements towards the slowest collapsing directions at larger scales.

LG pairs are located in a narrow range of local overdensity, ellipciticy and prolateness.
And this is consistent with the narrow mass range selection of specific samples.

The LG spin and orbital angular momentum have no particular alignment,
and we see no significan alignments in our LG pairs, however for the alignment
between pair spins we found a slight alignment signature for $2\sigma$ sample as
can be seen in figure $5$.

These alignment features are in agreement with the scenario that pairs 
created in-situ or falling into a filament/wall align their orbits with 
the large scale structure in a relaxation process where pair members
tend to moves along the slowest collapsing directions.
However, the most intriguing feature is the dependence of this alignment
with how close we represent the LG, is still not clear.
We explore if the pair masses are responsible of this, but we found 
no dependence at all.

>>>>

\begin{abstract}
We explore the characteristics of the Local Group (LG)
location in the cosmic web using a cosmological simulation in the
$\Lambda$CDM cosmology.  We use the Hessian of the gravitational
potential to classify regions in the cosmic web as a peak, sheet,
filament or void.  The LG is represented by two samples of halos
pairs. The first is a general sample composed by halo pairs with
similar masses and isolation criteria as observed in the LG.  The
second is a subset with additional kinematic constaints. We find that
the pairs in the LG sample with all constraints are: i) Preferentially
located in filaments and sheets, ii) located in in a narrow range of
local overdensity $0<\delta<4$, web ellipticity $0.1<e<1.0$ and
prolateness $-0.5<p<0.5$.  iii) Clearly aligned with the cosmic web,
in particular for pairs in filaments/sheets the orbital angular
momentum tends to be perpendicular to the filament direction or the
sheet plane. A stronger alignment is present for the vector linking
the two halos, which lies along the filament or the sheet plane.  We
show that the first and second results are expected trends with the LG
total mass. However, the strong alignment with the cosmic web cannot
be explained by a simple mass dependency.

@@

\subsection{Alignments withthe cosmic web}

We now study different alignments of the LG with respect to the cosmic web.

{\bf Orbital Angular Momentum}. Figure \ref{fig:alignment_n} shows the
cumulative distribution of $\mu\equiv\hat{e}_i\cdot\hat{n}$  for the
three eigenvectors $i=1,2,3$.    
Lines in each panel correspond to different samples.
The straight line across the diagonal shows the expected
result for vectors with randomly distributed directions.

There are two important features in Figure \ref{fig:alignment_n}.
First the alignments themselves. 
There is a strong anti-alignment signature between $\hat{n}$ and the
third eigenvector. 
With respect to the second eigenvector the distribution is consistent
with no aligment. 
For the first eigenvector there is a strong alignment, an expected
result after considering the results with the other eigenvectors and
keeping in mind that the eigenvectors are orthonormal.
Second, the alignment strenght changes for the different samples. 
For the anti-alignment with $\hat{e}_3$ the signal strenghtens as we
move from the GS to the 3$\sigma$ into the 2$\sigma$ sample.

Quantitatively, the anti-alignment feature found with the $\hat{e}_3$ 
vector means that for 2$\sigma$ sample, $\sim 50\%$ pairs have
$|\mu|<0.2$ ($78$ degrees angle), and $\sim 75\%$ pairs have $|\mu|<0.4$
($66$ degrees angle). 
These signals do not change significantly on
different environments as has been already show in different alignment
studies that similar \citep{Libeskind2013} or identical
\citep{ForeroRomero2014} web finding techniques as ours.
In particular  these trends hold for pairs in filaments and walls.
If we consider only pairs in filaments, we have that the pair orbital
angular momentum tends to be perpendicular to the filament direction,
in the case of sheets it tends to lie perpendicular to the sheet plane.

@@

{\bf Radial Vector}.  Figure \ref{fig:alignment_r} presents the
results for the eigenvectors alignments with respect to the vector
connecting the two halos. 
In this case we find that the vector $\hat{r}$
is strongly aligned along the direction defined by
$\hat{e}_3$ and anti-aligned along $\hat{e}_1$; correspondingly the
signal along $\hat{e}_2$ is rather weak.

We also find a stronger signal as we move into more restrictive
samples, although the signal from the GS is already very
significant. 
Quantitatively, the alignment feature with $\hat{e}_3$
means that for the 2$\sigma$ and 3$\sigma$ samples, $\sim 50\%$ pairs
have $|\mu|>0.8$ ($36$ degrees angle) and $\sim 25\%$ pairs have
$|\mu|<0.95$ ($18$ degrees angle).

@@

{\bf Halo Spin}. We also explore the alignment of the  angular
momentum (spin) of each pair member $\hat{j}_A$ and $\hat{j}_B$ with
each other, the orbital angular momentum and with the cosmic web.

Figure \ref{fig:jj_alignment} shows the cumulative distribution of dot
product between angular momentum of the  two halos. We find a a slight
alignment of spin vectors for the $2\sigma$ sample with a median around
$|\mu|\sim 0.7$ ($45$ degrees) However, we found no significant
alignment with the orbital angular momentum nor the cosmic web. This
is also consistent with recent results that show that the spin
alignment of halos of masses around $10^{12}$\Msun is very weak
\citep{ForeroRomero2014}.

@@

The mass range of the LG pairs is tightly correlated with the
properties of the web where they reside as shown in Table
\ref{table:web_type} and Figure \ref{fig:median_fraction}. Recent
analytical \citep{Alonso2014} and numerical studies \citep{Metuki2014}
have shown that the local overdensity is the dominant web property
that define the abundance and properties of halos. Quantities derived
from the tidal tensor play a secondary role.

Therefore, in our case, the fact that the preferred LG total mass is
around $1-4\times 12^{12}$\Msun implies that the preferred environment
are filaments and sheets with an overdensity close to the average
value, with values for the ellipticity and prolateness also correlated
with the overdensity.

However, there are alignment signals with the cosmic web that are not
mass dependent and seem to be stronger for different LG samples. There
is a clear anti-alignment between the third eigenvector and the
orbital angular momentum vector, meaning that this vector is
perpendicular to filaments and the sheets, depending on the
particular web environment. We also found that the vector joining the
LG halos are aligned with the third eigenvector; i.e. the pair is
aligned with the filaments and lies on the sheets.

These alignment features are in agreement with the scenario that pairs 
created in-situ or falling into a filament/wall align their orbits with 
the large scale structure in a relaxation process where pair members
tend to moves along the slowest collapsing directions.

The most interesting feature is that these alignments are
tighter as we narrow the kinematic conditions of the LG towards the
observed values. A deeper understanding requires the study of the full
formation history and coevolution with the cosmic web, a task beyond
the scope of the work presented here.
